Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit summary

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlight the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with previous 2-D modeling results from \citet{Huang2013a}.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
	\citealt{DSouza2015}), 
	We notice that the stacked image sometimes fails to recover the ellipticity 
	profile, probably due to the uncertainties in aligning galaxies before the 
	stacking process.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Envelopes}
    \label{ssec:twophase}

@@

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly depend on their stellar mass 
    (e.g. \citealt{RodriguezGomez2016} \addref{}). 
    The increasingly more prominent stellar halos in more massive galaxies could 
    reflect this point, assuming the stars in the outskirts are dominated by accreted 
    ones.  
    The negative color gradients we see in these massive galaxies may support this 
    assumption. 
    The slightly bluer color in their outskirts are consistent with the picture that 
    the stars there are from less massive galaxies on the ``red-squence''.

>>>>

	The ellipticity of the isophote contains information about the 3-D geometry 
	(e.g. \citealt{Chang2013, Mitsuda2017}) and kinematic (e.g. 
	\citealt{Cappellari2012, Weijmans2014}) of stars in massive galaxies.  
	The left panel of Fig \ref{fig:ell_color} shows the ellipticity profiles of HSC 
	massive galaxies and highlight the median profiles for the same three \mtot{} 
	bins used in Fig \ref{fig:avg_prof}. 
	In general, the ellipticity of massive galaxy slowly increases with radius.
	One can even notice this trend by directly comparing the shape of galaxy between 
	SDSS and HSC images (e.g. Fig \ref{fig:sdss_compare}).  
	More interestingly, the ellipticity profiles clear depend on \mtot{}: 
	at ${\sim} 10$ kpc, median ellipticities from all three bins are low and similar 
	($< 0.2$); but more massive galaxies become increasingly more elongated in their
	stellar halo. 	
	For the \logms{}$>11.8$ galaxy, its median ellipticity profile becomes steeper 
	at $>10$ kpc, and the ellipticity steadily increases from $e\le 0.2$ to 
	$e{\sim} 0.4$ at 50-60 kpc.
	This is consistent with studies of nearby massive galaxies, both from 1-D 
	ellipticity profiles and 2-D modeling results \citep{Gonzalez2005, 
	Huang2013a, Spavone2017}.
	Although this phenomenon was well-documented, clear evidence of mass-dependent
	ellipticity profiles and the potentially anti-correlated slopes of \mden{} and 
	ellipticity profiles has not been identified.
	If accreted stars dominate the stellar halos of massive galaxies, this 
	mass-dependent ellipticity profile may lead us to some insights about the 
	differences in their assembly history (e.g. average time since last merger, 
	average merger mass ratio).
	Previous simulations often focused on reproducing the rounder average shape 
	and slow-rotating nature of massive ETGs (e.g. \citealt{Wu2014}), the projected 
	ellipticity profiles and their correlations with the kinematic of stars and 
	merging history have not been well explored. 
	We also compare our ellipticity profiles with previous ones that are based on 
	image stacking techniques (the PSF-removed $i$-band from \citealt{Tal2011}, 
	the concentration galaxies with $11.0<$\logms{}$<11.4$ from 
	\citealt{DSouza2015}), 
	We notice that the stacked image sometimes fails to recover the ellipticity 
	profile, probably due to the uncertainties in aligning galaxies before the 
	stacking process.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{The ``Two phase'' Formation Scenario of Massive Galaxies and the 
            Build-Up of Outer Halos}
    \label{ssec:twophase}

@@

    State of the art hydrodynamic simulations of massive galaxy formation predict 
    that the fraction of accreted stars should strongly increase with their stellar 
    mass and the ``ex-situ'' component dominate the stellar halo (e.g.
    \citealt{RodriguezGomez2016} \addref{}). 
    This picture is supported by the increasingly more prominent stellar halos in 
    more massive galaxies and the negative color gradients we see in these massive 
    galaxies. 
    The slightly bluer color in their outskirts are consistent with the picture that 
    the stars there are from less massive galaxies on the ``red-squence''.

    Also under this picture, the shape of the stellar halo should keep fossil record

    As for the shape of the stellar halo,

    Tidal shocking and stripping during merger with the cD galaxy: the massive galaxies in the substructure generally interact with the cluster centre and the cD galaxy on near-radial orbits
